On the performance of the MAC model

### 2018-10-30 2018_nips_vigil/mac.tex
update on MAC part

The MAC network~\cite{hudsonManning18} is a recurrent model that performs reasoning 
using multiple steps, where each step involves sequentially analyzing a part of the question following which attention on the image is changed suitably.
At the end, a suitable answer is given based on this composite reasoning.
To improve the accuracy of prediction, both the questions and images
are preprocessed suitably. For the question,  a word-embedding is first used to
transformed the question into a sequence of vectors which is then passed through
a bidirectional LSTM to produce a sequence of hidden state pairs. Each such pair 
corresponds to a unique word in the question and is called the 
\emph{contextual embedding} for that word.
Similarly each image is initially processed using a pre-trained network (using ResNet) followed by two trainable CNN layers.

>>>>

The MAC network~\cite{hudsonManning18} is a recurrent model that performs reasoning 
using multiple steps, where each step involves sequentially analyzing a part of the question following which attention on the image is changed suitably.
At the end, a suitable answer is given based on this composite reasoning.
To improve the accuracy of prediction, both the questions and images
are preprocessed suitably. For the question,  a word-embedding is first used to
transformed the question into a sequence of vectors which is then passed through
a bidirectional LSTM to produce a sequence of hidden state pairs. Each such pair 
corresponds to a unique word in the question and is called the 
\emph{contextual embedding} for that word.
Similarly each image is initially processed using a pre-trained network (using ResNet) followed by two trainable CNN layers.\\
The core of network is a sequence of recurrent MAC cells. A MAC cell (Figure 1) is performing one reasoning step. At every step the network is driving the attention on one part of the question and a corresponding part of the image. This operation is made possible by the combination of 3 units working together, a control unit, a read and a write units. The control unit is updating the control state and drives the attention over the question. Given this control state, the read unit then retrieves information from the memory and drives the attention over the image.
Finally, the write unit retrieves this visual information and update the memory state.
The last part of the network is the output unit. The output unit is simply a classifier that process the concatenation of the question representation and the final memory to produce a final answer.\\
By going through this recurrent process, the network performs a reasoning strategy that learns concepts and relations between them. 
MAC is performing state of the art accuracy on CLEVR....
